Distill and Github Pages Setup

### 2022-02-01 _academics/ps753-glossary/ps753-glossary.Rmd
Text tweaks

vacuously transitive triad
: a triad where (5 of 16 possibilities)

intransitive triad
: a triad where (7 of 16 possibilities)

transitive triad
: a triad where (4 of 16 possibilities)

>>>>

vacuously transitive triad
: a triad where (...) (5 of 16 possibilities)

intransitive triad
: a triad where (...) (7 of 16 possibilities)

transitive triad
: a triad where (...) (4 of 16 possibilities)

### 2022-02-01 _meta/distill-and-github-pages-setup/distill-and-github-pages-setup.Rmd
Text tweaks, build
Text tweaks

Although it's intended to be complete, and not overly technical where avoidable, it does assume a modest level of comfort using basic tools like RStudio and GitHub. If you're on Mac or Linux, you probably have [git](https://git-scm.com/) built in already, but you might need to install it if you're on Windows. That's outside the scope of this article, but you can find information about it on the main Git page.

@@

Then load the library, which you should also do any time you want to work on your site in the future after opening the project:

@@

You could just go from here, if you're content with the URL GitHub chose for you. Your basic workflow will be:
- Work on content in RStudio
- Commit changes with git as you go
- Build the site when you're ready (or as often as you like)
- Push the changes to GitHub, which publishes them to your site.

>>>>

Although it's intended to be complete, and not overly technical where avoidable, it does assume a modest level of comfort using basic tools like RStudio and GitHub. If you're on Mac or Linux, you probably have [git](https://git-scm.com/) built in already, but you might need to install it if you're on Windows. That's outside the scope of this article, but you can find information about it on the [Git for Windows download page](https://git-scm.com/download/win).

The very high-level overview of the process here is:

1. Create a new, empty GitHub repository that will contain your site
2. Create a new, empty RStudio project using the repository you just created
3. Install the Distill framework into this project
4. Configure and build the bare-bones, empty site and push it up to GitHub
5. Configure GitHub Pages to publish the site

Once you've done that, you can begin writing content and publishing blogs, and spend time fine-tuning and tweaking your site. (You can also do that before setting up GitHub Pages if you want to wait to unveil it until it has more content and polish - as you prefer.)

@@

Then load the library, which you should also do as your first step (after opening the project) any time you work on it in the future:

@@

You could just go from here, if you're content with the URL GitHub chose for you. Your basic workflow will be:

- Work on content in RStudio
- Commit changes with git as you go
- Build the site when you're ready (or as often as you like)
- Push the changes to GitHub, which publishes them to your site.
